---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# common

<!-- badges: start -->
<!-- badges: end -->

The goal of *common* is to detect common elements among vectors and expand those
vectors by adding elements from each other.

## Installation

You can install the current version of *common* with:

```r
# install.packages("remotes")
remotes::install_github("ramiromagno/common")
```

## Motivation

I created this package to perform one specific task: to detect common elements among vectors and complete those
vectors by adding elements from each other, in a sort of guilty by association fashion. Note that the commonality is determined iteratively as new elements are added to vectors.

## Example

Here is the visual example:

![](man/figures/readme_fig01_wo_fonts.svg)

And the corresponding code:

```{r}
library(common)

lst <- list(v = c('a', 'b', 'c', 'd'),
            w = c('c', 'd', 'e', 'f'),
            x = c('f', 'g', 'h'),
            y = c('i', 'j'),
            z = c('j', 'k')
            )

lst2 <- complete_by_common(lst)
lst2
```

Note that while vectors `v` and `x` do not have any elements in common, `v` and `w`, and `w` and `x` do, and thus after we expand `v` to include elements from `w` (namely, `'f'`), then `v` and `x` also have common elements and are expanded accordingly.
